Numerous variables relating to 2016 election in 2021 US GSS

### 2022-03-19 outputs/paper/paper.Rmd
ggplot and glimpse of writing

---
title: "Numerous variables relating to 2016 election in 2021 US GSS"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk 
thanks: "Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git".
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

# Introduction

Donald Trump won the 2016 United States presidential election. We are not US citizens. 
However, considering

# Data
1.Conveying a sense of the dataset of interest.
2.Dicussion of the survey's methodology and its key features, strengths, weaknesses.
For instance what is the population, frame and sample.
How is the sample recruited 
what sampling approach is taken
what are some of the trade offs of this 
how is non response handled.
(What is good and bad about it)

@@

reduced_data$tax <- factor(reduced_data$tax, levels = c("Too low","About right","Too high"))
reduced_data %>%
  ggplot(aes(x = tax, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate")

```
US demographics: White 76.3%, Black: 13.4%, American Indian: 1.3%, Asian: 5.9%, Hispanic: 18.5%
https://www.census.gov/quickfacts/fact/table/US/PST045221.
Considering the result above, our data sample is fairly recruited.

@@

# Results
Convey findings.

@@

Things that we must include

>>>>

---
title: "Numerous variables relating to 2016 election in 2021 US GSS"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk 
thanks: "Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git".
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence (what was done). Second sentence(what was found). Third sentence (why this matters). Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

# Introduction
1) broader context to motivate
2) some detail about hat the papaer is about
3) a clear gap that needs to be filled
4) what was done
5) what was found
6) why it is important
7) The structure of the paper
(3~4 paragraphs)
Donald Trump won the 2016 United States presidential election. We are not US citizens. 
However, considering

# Data
A sense of the datasets should be communicated to the reader.
All varaiables should be throughly examined and explained.
Explain if there were similar datasets that could have been used and why they were not.
Why did we clean some variables?
what the variables look like using graphs or tables discussion of the observations.
Summary statistics should also be included

@@

reduced_data$Immigration <- factor(reduced_data$Immigration, levels = c("Strongly disagree","Disagree", "Neither","Agree","Strongly agree"))
reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "blue", "Trump" = "red", "Other" = "green", "Did not vote" = "yellow")) +
  labs(fil = "Candidate") +
  coord_flip()

```

# Results
Summary statistics, tables, graphs, images .... 
Regression tables must not contain stars??

Thesis: what triggered U.S citizens to vote Clinton and Trump.

US demographics: White 76.3%, Black: 13.4%, American Indian: 1.3%, Asian: 5.9%, Hispanic: 18.5%
https://www.census.gov/quickfacts/fact/table/US/PST045221.
Considering the result above, our data sample is fairly recruited.

@@

@@

what is done in this paper?
what is something that we learn about the world
what is another thing that we learn about the world
what are some weaknesses of what was done?
what is left to learn or how should we proceed in the future?
